
\documentclass[12pt]{article}
%	options include 12pt or 11pt or 10pt
%	classes include article, report, book, letter, thesis

\usepackage[margin=0.5in]{geometry}

\setlength{\parindent}{0pt}

\usepackage{hyperref}

%for writing of code in blocks like
%\begin{lstlisting}
%   .......
%\end{lstlisting}
\usepackage{listings}
\usepackage{color}
\usepackage{enumitem}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=C++,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}
%%%%%%%%%%%%%%%%%%%%%%

\title{Life of a Particle : Quiz 4}
\author{Sam Meehan}
\date{Due Date : 12 January 2017}

\begin{document}
\maketitle

\textbf{Question 1 : GitHub}
Perform the following steps to create GitHub repository.  Feel free to use the internet to search for how to do this if you don't remember.
\begin{itemize}[noitemsep]
\item Create a GitHub repository using the online interface at \href{https://github.com}{github.com} - be sure to include a README.md file when you create this repository.  Call the repository ``quiz4\_NAME'' where NAME is your name.  Remember, \textit{NO SPACES}!
\item Clone this repository to your laptop (\small{\ttfamily{git clone}})
\item Go into this respository directory (\small{\ttfamily{cd}}) and write a file called \textit{mycode.py} that contains some python code.  What that code does is not of importance.
\item Add this file to the repository for it to be tracked (\small{\ttfamily{git add <filename>}}).
\item Check the status of the repository to make sure that the file is ready to be uploaded (\small{\ttfamily{git status}})
\item Commit these changes to the repository (\small{\ttfamily{git commit -m ``Commit message here''}})
\item Push these changes to the external repository on \href{https://github.com}{github.com} (\small{\ttfamily{git push origin master}})
\end{itemize}
When you have pushed this and verified that the file you created exists online, you will submit the URL of this repository when replying to the email.  If you are successful in this, when solving the rest of the questions, please submit the solutions by adding them to your GitHub repository 
\newline
\newline
\textbf{Question 2 : Swapping}
This code will sum the numbers in the list $x$ :
\begin{lstlisting}
x=[2,1,4,3,5,7,4]
sum = 0
for i in range(len(x)):
	sum = sum+x[i]
print ``The sum is : '',sum
\end{lstlisting}
Given the two lists of numbers below, write the code, test it and upload it to the GitHub repository that you have created.  This code should calculate the sum of the element-wise product of the two lists $x$ and $y$.  If this is confusing wording, what we want to calculate is $$Sum=\sum_{i=0}^{N-1} x_{i}y_{i}$$ where $N$ is the number of elements in the lists $x$ and $y$.
\begin{lstlisting}
x=[2,1,4,3,5,7,4]
y=[6,1,0,3,2,-1,8]
\end{lstlisting}
















\end{document}